### 2018-09-23 ApproxComp/TKDE/sec-beyond.tex

It is worth pointing out that for all kind of techniques big data analytics, various computing resources should be seriously considered, \eg using bounded resources for approximation~\cite{CaoF17} and for incremental computation~\cite{abs-1801-01012}. Further, theoretical analyses are also important for developing approximation techniques. For instance, our query and data approximation techniques are based serious theoretical results~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaFLWCH16,MaFLWCH17}.

>>>>

It is worth pointing out that (1) for all kind of techniques big data analytics, various computing resources should be seriously considered, \eg using bounded resources for approximation~\cite{CaoF17} and for incremental computation~\cite{abs-1801-01012}, and (2) theoretical analyses are also important for developing approximation techniques. For instance, our query and data approximation techniques are based serious theoretical results~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaFLWCH16,MaFLWCH17}.

### 2018-09-23 ApproxComp/TKDE/sec-introduction.tex

\item[(3)] {\em Approximation computing} is a recent computation technique that returns a possibly inaccurate result rather than a guaranteed accurate result from a system point of view.  It involves with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}. Recently, a workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.  (see \eg 2016\footnote{\small \url{http://approximate.computer/wax2016/}}, 2017\footnote{\small  \url{http://approximate.computer/wax2017/}} and 2018\footnote{\small \url{http://approximate.computer/wax2018/}}). Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing. For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared with the fully accurate classification~\cite{Mittal16b}
\ei

>>>>

\item[(3)] {\em Approximation computing} is a recent computation technique that returns a possibly inaccurate result rather than a guaranteed accurate result from a system point of view.  It involves with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}. Recently, a workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.  (see \eg 2017\footnote{\small  \url{http://approximate.computer/wax2017/}} and 2018\footnote{\small \url{http://approximate.computer/wax2018/}}). Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing. For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared with the fully accurate classification~\cite{Mittal16b}
\ei
